---
title: "Unit 1 - 3 Review Starter"
author: "Technologic"
date: "2/23/23"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
sites <- read_csv("data/sand_minerals.csv")
location_descriptions <- read_csv("data/location_descriptions.csv")
density <- read_csv("data/density.csv")
solubility_hardness <- read_csv("data/solubility_hardness.csv")
```

## Exercises

### Exercise 1

```{r inspect-sand-minerals}
glimpse(sites) %>% 
  ls()
```

There are `r nrow(sites)` rows and `r ncol(sites)` columns in this dataset. Each row is stating the location and the types of minerals in each location. 

### Exercise 2

```{r inspect-other-dataframes}

glimpse(location_descriptions)
glimpse(density)
glimpse(solubility_hardness)

ls(location_descriptions)
ls(density)
ls(solubility_hardness)

```

Location_descriptions has `r nrow(location_descriptions)` rows and `r ncol(location_descriptions)` variables.
Density has `r nrow(density)` rows and `r ncol(density)` variables.
Solubility_hardness has `r nrow(solubility_hardness)` rows and `r ncol(solubility_hardness)` variables.

Each row in location_descriptions is a type of environment for each location site #.
Each row in density is a specific mineral and its density.
Each row in solubility_hardness is a specific mineral with its hardness and solubility specified.

### Exercise 3
```{r join-mineral-properties}

sand_mineral_density<-
sites %>% left_join(density)

sand_mineral_properties<-
sand_mineral_density %>% left_join(solubility_hardness)
```

The output has 23 rows which is the same number as sand minerals.

### Exercise 4

```{r count-sand-mineral-observed-per-location}
sand_mineral_properties %>%
  count(location) 
  
```

```{r sand-mineral-properties-location-slice-max}
sand_mineral_properties %>% 
  slice(1:13)
```

```{r sand-mineral-properties-density-slice-max-desc}
sand_mineral_properties %>% 
  arrange(desc(density)) %>% 
  slice(1:13)
```

```{r sand-mineral-properties-location-hardness}
sand_mineral_properties %>% 
  select(location, hardness) %>% 
  slice(1:18)
```

```{r sand-mineral-properties-NA-omit-desc-density}
sand_mineral_properties %>% 
  na.omit(hardness) %>% 
  arrange(desc(density)) %>% 
  slice(1:18)
  
```


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

## Part II - Data Visualization

`starwars` is already loaded within the `dplyr` package (within `tidyverse`)

### Exercise 7

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 8

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.

### Exercise 9

Remove this text, and add your answer for Exercise 6 here.
Add code chunks as needed.
Don't forget to label your code chunk.
Do not use spaces in code chunk labels.
